---
title: "simpleRegress"
author: "Kaylie Brehm"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```

## Length to Neck Model  

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

The graph shows a somewhat weak, but still positive correlation between the length of bear and size of neck. There are plenty of outliers that do not aline well with the line of best fit.

The adjusted R-square of this data is about 0.75.

## Prediction Model 

### (for the length of a bear who has a neck of 17, 22 and 26)


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE)
```

The prediction for the height of a bear with a neck size of 17 is about 52.8. The prediction for the height of a bear with a neck size of 22 is about 70.0. The prediction for the height of a bear with a neck size of 26 is about 67.6. The df value for this prediction chart is 52. The residual scale value is about 5.4.

## Length to Chest Model

```{r}
chesty <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(chesty)
summary.lm(chesty)
```

The graph shows a stronger, still positive correlation between the length of bear and size of chest. There are not as many outliers along the line of best fit.

The adjusted R-square of this data is about 0.79.


## Prediction Model 

### (for the length of a bear who has a chest of 17, 22 and 26)

```{r}
new <- data.frame(CHEST=c(17,22,26))
predict(chesty,new)
predict(chesty,new,se.fit=TRUE)
```

The prediction for the height of a bear with a chest size of 17 is about 39.6. The prediction for the height of a bear with a chest size of 22 is about 44.7. The prediction for the height of a bear with a chest size of 26 is about 48.8. The df value for this prediction chart is 52. The residual scale value is about 4.9.


# Conclusion

The adjusted R-square for the chest model is 0.79 while the adjusted R-square for the neck model is 0.75. The better model is the chest one because the adjusted R-square value is higher.


